\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[T1]{fontenc}

\title{ARSandbox Traffic Simulation Install Guide}
\author{Team 56}
\date{April 2019}

\begin{document}

\maketitle

\section{System Requirements}
    \begin{itemize}
        \item Microsoft Kinect V2 Sensor.
        \item 1080p Webcam.
        \item A mini short-throw projector.
        \item Intel Core I7 or equivalent processor.
        \item 8+ GB RAM.
        \item GTX 1080 Graphics Card (Other cards may likely work, but are untested).
        \item An elevated sandbox with approximately 200 lbs. of play sand and an overhead mount for the projector, webcam and Kinect. 
    \end{itemize}
    
\section{Install Unity}
\begin{itemize}
    \item Go to url{https://unity3d.com/get-unity/download} and download Unity version 2018.3.12.
    \item Execute the downloaded installer and follow the instructions given.
    \begin{itemize}
        \item During installation, ensure that the “Vuforia Augmented Reality Support” option is enabled.
    \end{itemize}
\end{itemize}

\section{Install SUMO}
\begin{itemize}
    \item Go to \url{https://sumo.dlr.de/wiki/Installing#Windows} and download the 64 bit Windows installer.
    \item Execute the installer and follow the instructions.
    \begin{itemize}
        \item When prompted, select “C:\textbackslash Sumo\textbackslash” as the installation location
        \item Follow the websites instructions to add SUMO to the PATH on your computer and add the environment variable SUMO\_HOME. For more information or help please visit the following webpage. \url{https://sumo.dlr.de/wiki/Basics/Basic_Computer_Skills}
    \end{itemize}
    
\end{itemize}

\section{Clone the repository}
    \begin{itemize}
        \item  \url{https://github.com/spencjon/AR-Sandbox-for-OSU-Civil-Construction-Engineering.git}
    \end{itemize}

\section{Open one of the two scenes in Unity}
\begin{itemize}
    \item For Traffic Simulation mode, open \textbackslash src\textbackslash AR\_Sumobox\textbackslash Assets\textbackslash Scenes\textbackslash SampleScene.unity
    \item For Depth, Design, and Cut \& Fill modes, open \textbackslash src\textbackslash AR\_Sandbox\textbackslash Assets\textbackslash Scenes\textbackslash Sandbox.unity
\end{itemize}

\section{Ensure Vuforia is enabled}
\begin{itemize}
    \item Open File > Build Settings
    \item Select “Player Settings”
    \item Expand “XR Settings”
    \item Make sure that “Vuforia Augmented Reality” is checked
    \item If the checkbox is not available, do the following:
        \begin{itemize}
            \item Click “Vuforia Augmented Reality” under “XR Support Installers”
            \item Run the program that is downloaded and follow the instructions (you will need to close Unity to finish the installation)
            \item Reopen the scene in Unity
        \end{itemize}
\end{itemize}
\end{document}
